Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-05 ProbabilisticCoherence.tex
Old Section 2 merged with coherence section

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.  To describe these we use the small hierarchy in Figure~\ref{fig1}. In the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level (Series {\em AA}, {\em AB}, {\em BA} and {\em BB}) and then summed to recover all top level-series.  Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series {\em Tot}) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast. A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series {\em A} and {\em B}.

@@

The remainder of the papers is  structured as follows.   In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.  In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.  Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.  In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.

@@

\section{Hierarchical Time Series}\label{sec:notation}

In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.  A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables.  For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.  The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.

We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$,  and $\bm{b}_t \in \mathbb{R}^m$ is a vector comprised of observations of all bottom-level series at time $t$. The hierarchical structure of the data imply the following holds for all $t$
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.  For the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and 
$$ 
  \bm{S} = \begin{pmatrix} 
               1& 1 &1 &1  \\ 
               1 &1 & 0 &0 \\   
               0&0  & 1 & 1 \\ 
               & \multicolumn{2}{c}{\bm{I}_4} &   
           \end{pmatrix}, 
$$

@@

\section{Coherent forecasts}\label{sec:definitions}

@@

>>>>

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.  To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$
and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.  In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all top level-series.  Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast. A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.

@@

The remainder of the papers is  structured as follows.  In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.  Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.  In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.

@@

%\section{Hierarchical Time Series}\label{sec:notation}
\section{Coherent forecasts}\label{sec:definitions}
\subsection{Notation and Preliminaries}\label{sec:notation}

Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.  A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.  The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.  The hierarchical structure of the data imply the following holds for all $t$
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.  For the hierarchy in Figure~\ref{fig1}
$$ 
  \bm{S} = \begin{pmatrix} 
               1& 1 &1 &1  \\ 
               1 &1 & 0 &0 \\   
               0&0  & 1 & 1 \\ 
               & \multicolumn{2}{c}{\bm{I}_4} &   
           \end{pmatrix}, 
$$

@@

\subsection{Coherent Point Forecasts}\label{sec:cohpointf}

@@

\subsection{Coherent Probabilistic Forecasts}\label{sec:cohprobf}
